Quantifying uncertainty in Pareto lake area estimates

### 2021-05-15 manuscript/manuscript.Rmd
msu->UW

---
title: Estimating Uncertainty in Global Lake Area

author:
  - name: Joseph Stachelek
    affiliation: a
address:
  - code: a
    address: Department of Fisheries and Wildlife, Michigan State University, East Lansing, MI, USA

>>>>

---
title: Quantifying uncertainty in Pareto lake area estimates

author:
  - name: Joseph Stachelek
    affiliation: a
address:
  - code: a
    address: Center for Limnology, University of Wisconsin-Madison, Madison, WI, USA
